Fluent statistical computing interfaces for biological data analysis

### 2020-03-24 Rmd/05-embeddings.Rmd
update text

The `liminal` software is implemented as an open source R package @baseR. All
visualisations produced by the package were constructed using the `vegawidget`
package, which is an R interface to the Vega-Lite grammar of interactive
graphics. Ensemble graphics for arranging tour and embedding views are
generated using the `shiny` packages. We have made extensive use of the `tourr`
package for constructing tour paths.

- **concatenated views:** see local and global structures
- **user interactions:** verify cluster shapes and locations
- **quality checks:** interrogate an embedding with reference
to the underlying data

@@

### Case Study 1: Exploring tree structured data

>>>>

We have implemnted the above design as an open source R package 
called `liminal` [@baseR]. The package allows analysts to constuct
concatenated visualisations, via the
Vega-Lite grammar of interactive graphics (using `vegawidget` package)
and provides an interface for constructing brushes and manipulating tour paths
using the `shiny` and `tourr` packages. `liminal` also provides a stand-alone
interface to the tour, in addition to the linked scatterplot interfaces 
discussed above. Below we display the `liminal` API, and our approach to
generating tour paths and user interactions.

@@

### Case Study 1: Exploring tree structured data with tours and t-SNE
